---
title: "PackageTutorial"
output: html_document
date: "2023-11-21"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## An Introduction to My R Package

This package contains functions that help clean up NA values, organize columns for easier viewing, create linear plots using any data set you have available, and plot any linear models by combining QQ and scatter plots of residuals vs fitted values. Most of these functions have an input test, and one has an output. During this tutorial feel free to try inputting the wrong column name, independent/dependent variables for some fun error messages.

In order to get the functions to work make sure you download and install the following packages.

```{r}
devtools::install_github(sdmancik/mancik2.pkg)
surveys <- read_csv("/cloud/project/data/surveys.csv")
crabs <- read_csv("/cloud/project/data/crabs.csv")

library(tidyverse)
library(ggplot2)
library(gridExtra)
library(dplyr)
library(broom)
library(jpeg)
```

For the last function, "Fun function" aptly named. We will have to download a jpeg.

```{r}
url <- "https://i.imgflip.com/1n7w77.jpg?a472488"
download.file(url, "1n7w77.jpg", mode = "wb")
```

## Utilizing the functions

There are five functions in this package and I will go over examples of each one.

## Clean NAs

This function is specific to cleaning up NA values out of data sets, in specific columns. This speeds up the process instead of having to write out code every single time you want to clean up these values.

The command for this function is clean_nas(data, "column") this allows you to specify whatever data set you want, as well as column.

For this tutorial we will be using the surveys.csv data set and for the column, weight.

## Augment

This function is used to re-order columns of a data set from low to high values descending. This can be usefull if you want to clean up some data to look more organized.

The command for this function is order_data(data, "column").

For this tutorial we will be using the crabs.csv data set.

## Linear Model

This function is used to create an Lm of any data set you want without having to type out the code and will be used in conjunction of the next function.

The command for this function is create_lm(data, dependent_var, independent_var)

We will be using the data set crabs, as well as the dependent variable "frontal_lobe" and independent variable "Latitude".

## Plot

This function will take any linear model that has been created and now combine two graphs into one to show the residual and fitted values. You could even take it a step further and add more graphs for other data, but I just wanted to show it was possible so I kept it to two for now.

The command for this function is info_plot(whatever you name your lm model) for this tutorial lets use the Lm in the last function for this.

Now the error test for this one is specifically for whatever model you try to input. So lets say you tried to use something other than a linear model. It would then give you the error message but for this tutorial I'm not going to have you create another input model just to test it out, you can do that yourselves if you want.

## FunFunction

This function is purposefully going to throw an error code just because we wanted to show that we could. This is where the jpeg you had to download comes in to play and in order to get it to work, I used the clean NAs function we started with. So now, if you input the wrong column name you will get another resulted error message instead.

The command for this function is, Fun_function(data, "column") So go ahead and try that now with the wrong column name or something that doesn't exist.

That's it, thank you everyone for staying with me so far and I hope you all have a wonderful evening.